\section{Publications}

\subsection{Books}
\mybook{Double Star Astrometry; Collaborations, Implementations, and Advanced Techniques}
    {Eds. Weise, Genet, and Wallen}
    {Collins Foundation Press}
    {Santa Margarita, CA}
    {2015}
\mybook{The Double Star Reader}
    {Eds. Clark, Genet, Johnson, Wallen, and Weise}
    {Collins Foundation Press}
    {Santa Margarita, CA}
    {2013}

\subsection{Papers}
``International Speckle Interferometry Collaboration'',
    Weise, et al., 
    Speckle Interferometry of Close Double Stars; Special Issue of the Journal of Double Star Observations. 
    Eds. Clark, Genet, Wallen, Legg, Genet. 
    Chapter 9. 
    Copyright 2015.\\
``Mt Wilson Meets the Double Image Micrometer’, 
    Weise, E., et al., 
    The Journal of Double Star Observations, 
    vol. 11, no. 3, pg. 170, 
    2015.\\
``Kitt Peak Speckle Interferometry of Close Visual Binary Stars'', 
    Genet et al., 
    Proceedings for the 33rd Annual Meeting of the Society for Astronomical Sciences, 
    Eds. Warner, Buchheim, Foote, and Mais, 
    pg. 77, 
    May 2014.\\
``Undergraduate Observations of Separation and Position Angle of Double Stars Ary6AD And Ary6AE at Manzanita Observatory'', 
    Hoffert et al., 
    Proceedings for the 33rd Annual Meeting of the Society for Astronomical Sciences, 
    Eds. Warner, Buchheim, Foote, and Mais, 
    pg. 225, 
    May 2014.\\
``Close Double Star Speckle Interferometry Program'', 
    Proceedings for the 32nd Annual Meeting of the Society for Astronomical Sciences, 
    pg. 61, 
    May 2013.\\
``Second Annual Apple Valley Double Star Workshop'', 
    Brewer et al., 
    The Journal of Double Star Observations, 
    vol. 10, no. 3, pg. 245, 
    2014.\\
``Apple Valley Double Star Workshop'', 
    Brewer et al., 
    The Journal of Double Star Observations, 
    vol. 10, no. 3, pg. 160, 
    2014.\\
``A Novel System for Classifying Binary Orbital Solutions'', Weise, E., and Genet, R., The Journal of Double Star Observations, vol. 11, no. 1S, pg. 219, 2015.
