\section{Teaching}
% TODO: ADD INTERNS

\teachingposition{Teaching Assistant}
    {Physics Lab: E\&M, Waves, and Optics}
    {Physics Department, UCSD}
    {Winter 2015} 
Led class demonstrations, guided students in completing experiments, and graded lab reports.

\teachingposition{Guest Lecturer}
    {Honors Astronomy}
    {Concordia University, Irvine, CA}
    {October 2014}
I was invited to lead a research project for the Honors science students of Dr. John Kenney at the Concordia University in Irvine, CA. As a guest lecturer I taught students how to observe double stars. The lecture was followed up with an observation session and a published paper:
``Undergraduate Observations of Separation and Position Angle of Double Stars Ary6AD And Ary6AE at Manzanita Ob- servatory'', Hoffert et al., Proceedings for the 33rd Annual Meeting of the Society for Astronomical Sciences, Eds. Warner, Buchheim, Foote, and Mais, pg. 225, May 2014.

\teachingposition{Teaching Assistant}
    {Astronomy 299}
    {Cuesta College, San Luis Obispo, CA}
    {Summer 2013}
Guided research projects for the class, involving making astonomical observations and writing lab reports.

\teachingposition{Teaching Assistant}
    {Astronomy 299}
    {Cuesta College, San Luis Obispo, CA}
    {Summer 2012}
Gave lectures on the birth and death of the universe, the HR Diagram, and historical methods of observing the stars.

\subsection{Teaching Seminars and Certifications}
\teachingseminars{Mapping Knowledge Gaps}
    {UC San Diego Teaching + Learning Commons}
    {7 October 2019}
