\section{Work Experience}
% TODO:
% \jobtitle{Software Developer}{Bloom...}{October 2019}{Present}

\jobtitle{Backend Engineer}{Bloom Health}{October 2019}{Present}
$\cdot$ Developed backend server software for Bloom Health's wellness iOS app.
$\cdot$ Leveraged AWS to run Swashbuckle server and process image data submitted by users.

\jobtitle{Lead Software Developer}{CureMetrix Inc.}{August 2016}{Present}
$\cdot$ Contributed to the successful FDA submission for a class 2 medical device, {\it cmTriage}.\\
$\cdot$ Maintained Traceability Matrix and developed Software Requirement Specifications.\\
$\cdot$ Packaged cancer detection software for deployment on Amazon Web Services (AWS).\\
$\cdot$ Maintained client accounts and ensured delivery of accurate and dependable results.\\
$\cdot$ Lead development team in feature integration and bug fixes for our cancer detection product, {\it cmAssist}.\\
$\cdot$ Guided interns in developing features for our products, including status tracking and security upgrades.\\
$\cdot$ Planned, architected, and deployed secure software to external clients using Amazon Web Services.\\
$\cdot$ Maintained the integrity of training and testing data that included over 2 million medical images and pathology data.

\jobtitle{Data Scientist}{CureMetrix Inc.}{November 2015}{August 2016}
$\cdot$ Researched and implemented techniques to detect and classify anomalies in medical images using neural networks.\\
$\cdot$ Used TensorFlow to train CNN, FRCNN, and FCN networks.

\jobtitle{Research Assistant (Intern)}{CureMetrix Inc.}{12}{23 October 2015}
$\cdot$ Assisted the CureMetrix research team with data curration and storage solutions.\\
$\cdot$ Wrote a software tool that estimates the amount of fibroglandular tissue visible in a mammogram.

\jobtitle{Gymnastics Instructor}{University of California, San Diego}{2011}{2018}
$\cdot$ Planned and lead weekly classes for adults and children.\\
$\cdot$ KnockAround Camp counselor.

\jobtitle{Canoe Guide}{Northern Tier High Adventure Base, Ely, Minnesota}{June 2011}{August 2011}
$\cdot$ Planned and guided over 400 miles of canoe treks.\\
$\cdot$ Responsible for the safety of scouts and chapperones.
